Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-25 paper.qmd
Added scripts for PBMC3k

<!--Fit the best model for author suggestion and compute error-->
```{r}
#| label: hexbin-pbmc
#| 
umap_pbmc_scaled_with_cluster <- read_rds("data/pbmc3k/umap_pbmc_scaled_with_cluster.rds")

@@

```{r}
#| label: combine-data-pbmc

@@

<!--best choice-->
<!--Fit the best model and compute error-->
```{r}
#| label: tsne-num-bins-pbmc
tsne_pbmc_scaled_best_with_cluster <- read_rds("data/pbmc3k/tsne_pbmc_scaled_best_with_cluster.rds")

>>>>

<!--Fit the best model for author suggestion and compute error-->
<!--pbmc3k/14_gen_model_with_UMAP.R-->
```{r}
#| label: hexbin-pbmc
#| 
umap_pbmc_scaled_with_cluster <- read_rds("data/pbmc3k/umap_pbmc_scaled_with_cluster.rds")

@@

<!--pbmc3k/11_gen_mse_for_diff_methods.R-->
```{r}
#| label: combine-data-pbmc

@@

<!--best choice-->
<!--Fit the best model and compute error-->
<!--pbmc3k/15_gen_model_with_tSNE.R-->
```{r}
#| label: tsne-num-bins-pbmc
tsne_pbmc_scaled_best_with_cluster <- read_rds("data/pbmc3k/tsne_pbmc_scaled_best_with_cluster.rds")
